### 2016-11-30 README.Rmd
removed unnecessary call to train option
new badge

---
output: 
  html_document: 
    keep_md: yes
---
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/pdp)](https://cran.r-project.org/package=pdp)
[![Build Status](https://travis-ci.org/bgreenwell/pdp.svg?branch=master)](https://travis-ci.org/bgreenwell/pdp)
[![Coverage Status](https://img.shields.io/codecov/c/github/bgreenwell/pdp.svg)](https://codecov.io/github/bgreenwell/pdp?branch=master)
[![Downloads](http://cranlogs.r-pkg.org/badges/pdp)](http://cranlogs.r-pkg.org/badges/pdp)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/pdp)](http://cranlogs.r-pkg.org/badges/grand-total/pdp)

@@

# Partial dependence of glucose and age on diabetes test result (neg/pos). This
# may take a couple minutes!
partial(pima.svm, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE,
        train = pima)
```

>>>>

---
output: 
  html_document: 
    keep_md: yes
---
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/pdp)](https://cran.r-project.org/package=pdp)
[![Build Status](https://travis-ci.org/bgreenwell/pdp.svg?branch=master)](https://travis-ci.org/bgreenwell/pdp)
[![Coverage Status](https://img.shields.io/codecov/c/github/bgreenwell/pdp.svg)](https://codecov.io/github/bgreenwell/pdp?branch=master)
[![Downloads](http://cranlogs.r-pkg.org/badges/pdp)](http://cranlogs.r-pkg.org/badges/pdp)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/pdp)](http://cranlogs.r-pkg.org/badges/grand-total/pdp)
[![Rdoc](http://www.rdocumentation.org/badges/version/pdp)](http://www.rdocumentation.org/packages/pdp)

@@

# Partial dependence of glucose and age on diabetes test result (neg/pos). This
# may take a couple minutes!
partial(pima.svm, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE)
```
